---
title: "It's time!"
author: "Misson Charlotte"
date: "10/14/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Context  
Some people in Herault (France) did analyse their urine, searching for an extreamly dangerous herbicid glyphosate.  
*What is the results of analysis?*  
**Every sample were positives for glyphosate!** The only difference is the rate of it in the samples.  
  
However the profile of "samples" is far from the results. For exemple, Gregory who's living as healthy as possible:  
- He eats only biological products (except meat),  
- He practices sport several hours a week,  
Despite this, the analysis of Gregory reveals that the rate of glyphosate is more than three times higher than the authorized dose!  

Angry at this results, 44 persons have filed a complaint at the republic persecutor of Montpellier. They are really upset against the politicians who accepted to renew the authorisation of salling and using that poison.   




When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## Bibliography
